Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-03-20 paper/main.tex
kill the orphan

Casares, Colcombet, and Fijalkow very recently introduced a structure
called \emph{alternating cycle decomposition
  (ACD)}~\cite{casares.21.icalp} which compactly represents the
information about all accepting and non-accepting automata cycles. We
expect that ACD could potentially be used to reduce the number of
acceptance marks or to simplify the acceptance condition. However,
such a reduction is not obvious.
%Moreover, the construction of ACD seems to be computationally expensive.

>>>>

Casares, Colcombet, and Fijalkow very recently introduced a structure
called \emph{alternating cycle decomposition
  (ACD)}~\cite{casares.21.icalp} which compactly represents
%the information about
all accepting and non-accepting automata cycles. We
expect that ACD could %potentially
be used to reduce the number of
acceptance marks or to simplify the acceptance condition. However,
such a reduction is not obvious.
%Moreover, the construction of ACD seems to be computationally expensive.
